Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
Updating scatter relationship

If the SMBH dominates the gravitational potential at the stagnation
radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
(\ref{eq:stag_analytic}) simplifies to
\begin{eqnarray}
  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
    9
 \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4
 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:stag_simple}
\end{eqnarray}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) leads to a similar scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$; (2) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK).  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows {\bf
  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.

>>>>

If the SMBH dominates the gravitational potential at the stagnation
radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
(\ref{eq:stag_analytic}) simplifies to
\begin{align}
  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
    9
 \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4
 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:stag_simple}
\end{align}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).

@@

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the strong sensitivity of the accretion rate
to the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (Fig.~NICK) (2) The
scatter introduced in using scaling relationships ($\Mbh-\sigma$) 
and ($\Mbh-L_{\rm bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.  The
combination of (1) and (2) is capable of explaining much of the
observed sample, especially considering that scatter in $L_{\rm X}$
due to variations in $\dot{M}$ is exacerbated by the expectation that
$\epsilon_{X} \propto \dot{M}$ for radiatively inefficient flows. At a
wind heating parameter there is an order of magnitude difference between
$\dot{M}$ for core and cusp galaxies at fixed $v_w$ and $M_{\bullet}$
(Fig.~\ref{fig:bh_growth}) which could also lead to scatter of $\dot{M}$ due
to the variation in the Nuker stellar density profile $\Gamma$ at
fixed $M_{\bullet}$. However, the \citet{Pellegrini10} find that the
scatter in $L_X$ is similar if one just looks at core/cusp galaxies separately.

{\bf
  AG Challenge: Scatter in $L_X$ is similar for cores and cusps in Perllegrini}.
